New Horizons University is a modern institution that is constantly striving to improve its processes, particularly with regard to student deliberation. In this thesis, we present an IT solution in the form of an application to help the university in this process.

Student deliberation is a complex process involving the analysis of several criteria, including academic performance. The application we are proposing takes this into account by tracking student data, such as course completions and transcripts. It also calculates percentages and generates a deliberation grid as well as personalized transcripts for each student.

The application facilitates jury decision-making by providing relevant information and simplifying the deliberation process. It also enables the university to gain time and efficiency in managing student data.

Our solution is the result of a careful analysis of existing practices and standards at other universities. It is therefore ideally suited to the specific needs of New Horizons University.

We have designed our application as an extensible solution, thanks to an API Rest that enables easy communication with other third-party services such as Moodle or Google Classroom. This flexibility ensures the solution's independence and scalability.

All in all, our application offers an effective and adapted solution for student deliberation, which will enable New Horizons University to modernize its processes and gain in efficiency while ensuring personalized student follow-up.
